---
title: "WUP_04"
author: "America Olivo"
date: "fall 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
wup04data <- read.csv(file = "GSScsv.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

The methods that will be used to analyze our variables is a boxplot and favstats. 
```{r eval=FALSE}
wup04data <- wup04data %>%
mutate(across(where(is.character), as.factor))
```

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(WORDSUM~DEGREE,data= wup04data)
```

Lt High school is different than junior college and graduate school but is smaller compared to high school and bachelors.  

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

``` {r}
favstats (WORDSUM~DEGREE, data = wup04data)
```
The median shows that Lt High school is different than all of the subjects except Junior College and Bachelor, which are similar.

## Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
model1 <-aov(WORDSUM~DEGREE,data= wup04data)
summary.aov(model1)
```

``` {r}
par(mar = c(3, 20, 2, 2))
plot(TukeyHSD ( model1, conf.level = 0.95),las=2)
```

There is a 95% of chance that they are similar expect Lt high school to  graduate and high school to graduate which are different.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


